### 2019-05-28 manuscrip_clean.Rmd
latest text comments addressed

@@

*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@mackie1987:uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] (Appendix 10). Since the sampling biases of ROV and gut content based methods are very different, the data were merged to the level of feeding guilds. The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), the large crustacean specialist (feeding on large decapods, mysids, or krill), the fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), the gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and the generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group). We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa and for *Nanomia* sp.  eating *Aegina*, since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear if the medusae were attempting to prey upon the siphonophores. Personal observations on feeding (from SHDH, CAC, and Philip Pugh)  were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*. We extracted copepod prey length data from [@purcell1984functions]. To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (Appendix 11).

@@

## Discussion {-}
  This core aim of this study is to characterize the evolutionary history of siphonophore tentilla and its relationships with diet. In addition, we produced novel findings on tentilla morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.

@@

  The evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution. This strategy is particularly important in open ocean ecosystems, a homogeneous abiotic environment where the only niche heterogeneity available is the potential interactions between organisms [@robison2004deep].

  The evolutionary history of siphonophore diets indicates that being a specialist was an ancestral aspect of their trophic niche, while trophic generalism is likely a derived condition. Several studies  (reviewed in [@futuyma1988evolution]) have suggested that resource specialization is an irreversible dead end due to the constraints posed by their phenotypic specialization. Our reconstructions show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times, and generalism has evolved independently at least twice.

@@

@@

  Some siphonophore clades have more nematocyst types than others in the tentacles (Tendiculophora has 4 types, Cystonectae and Apolemiidae have 1), or different subtypes (e.g. stenoteles, mastigophores, birhopaloids). Siphonophores bear nematocysts in different parts of the colony (tentacles, gastrozooids, papons, palpacles, bracts, nectophores, and gonozooids) [@totton1965synopsis]. In this paper we only look at the presence of nematocyst types in the tentacles, therefore the gains and losses reported are not necessarily morphological innovations, but developmental allocations. For instance, stenoteles (a type of heteroneme) are absent from the tentacles of *Physalia* and seem to reappear in Euphysonectae, but we know that *Physalia* has stenoteles in other body parts [@totton1965synopsis].

@@

  Siphonophores play a wide variety of predatory roles in the open ocean, ranging from mid-trophic small crustacean eaters to piscivorous super-carnivores. The morphological attributes of predators are often finely tuned for their performance during the capture of their prey. With the diversification of prey type specializations, comes the evolution of morphologies adapted to the challenges posed by different prey. Siphonophore tentilla and nematocysts display a plethora of forms, which are strongly associated with their prey type. The results presented here indicate that these associations are a product of correlated evolution in highly integrated traits. We conclude that the siphonophores were able to establish as abundant oceanic predators by occupying a variety of trophic niches through the evolution and diversification of extraordinary prey capture tools on their tentacles.

>>>>

  Coexisting siphonophores feeding on the same planktonic community are potential competitors. Traditional ecological coexistence theory [@simpson1944tempo] predicts that competition between species would select for increasing ecological specialization. Moreover, specialization is often thought to be an evolutionary ‘dead end,’ meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource in which they are specialized [@futuyma1988evolution]. However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution; @johnson2009competition], and resource switching [@hoberg2008macroevolutionary]. Here we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from different ancestral predatory specialists, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.

@@

*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] (Appendix 10). Since the sampling biases of ROV and gut content based methods are very different, the data were merged to the level of feeding guilds. The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), the large crustacean specialist (feeding on large decapods, mysids, or krill), the fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), the gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and the generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group). We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa and for *Nanomia* sp.  eating *Aegina*, since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear if the medusae were attempting to prey upon the siphonophores. Personal observations on feeding (from SHDH, CAC, and Philip Pugh)  were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*. We extracted copepod prey length data from [@purcell1984functions]. To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (Appendix 11).

@@

## Discussion {-}
  This core aims of this study are to examine the evolutionary history of siphonophore tentilla and diet, characterize the evolutionary shifts in their trophic niche, and identify the morphological characters that evolve with changes in prey type. We inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory, and whether the diets of siphonophores can be discriminated by observing their tentacles. In addition, we produced novel findings on tentilla morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.

@@

The evolutionary history of siphonophore diets indicates that being a specialist was an ancestral aspect of their trophic niche, while trophic generalism is likely a derived condition. Several studies  (reviewed in [@futuyma1988evolution]) have suggested that resource specialization is an irreversible dead end due to the constraints posed by their phenotypic specialization. Our reconstructions show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times, and generalism has evolved independently at least twice. Among the evolutionary hypotheses considered, we find support for both hypotheses (2) and (3), but no support for hypothesis (1). The evolutionary history of tentilla shows that siphonophores are an example of trophic niche diversification via morphological innovation and evolution. This strategy is particularly important in open ocean ecosystems, a homogeneous abiotic environment where the only niche heterogeneity available is the potential interactions between organisms [@robison2004deep].

@@

    Some siphonophore clades have more nematocyst types than others in the tentacles (Tendiculophora has 4 types, Cystonectae and Apolemiidae have 1), or different subtypes (e.g. stenoteles, mastigophores, birhopaloids). Siphonophores bear nematocysts in different parts of the colony (tentacles, gastrozooids, papons, palpacles, bracts, nectophores, and gonozooids) [@totton1965synopsis]. In this paper we only look at the presence of nematocyst types in the tentacles, therefore the gains and losses reported are not necessarily morphological innovations, but developmental allocations. For instance, stenoteles (a type of heteroneme) are absent from the tentacles of *Physalia* and seem to reappear in Euphysonectae, but we know that *Physalia* has stenoteles in other body parts [@totton1965synopsis]. Nonetheless, siphonophores have evolved unique nematocyst types, not present in any other cnidarian. For example, rhopalonemes (acrophores and anacrophores), and the haploneme homotrichous anisorhizas [@werner1965nesselkapseln]. Both these nematocyst types evolved in the stem to Tendiculophora, and are likely morphological innovations, since they have not been yet found in any other tissue of any other organism. The gain of extreme elongation in the haplonemes of Tendiculophora can be interpreted as part of the character shift to a novel anisorhiza subtype.

@@

@@

  Siphonophores have diverse predatory niches in the open ocean, ranging from mid-trophic small crustacean eaters to piscivorous super-carnivores. With the evolution of diversified prey type specializations, comes the evolution of morphologies adapted to the challenges posed by different prey. The results presented here indicate that the associations found between siphonophore tentilla and their prey are a product of correlated evolution in highly integrated traits. While much of the literature focuses on how predatory generalists evolve into predatory specialists, in siphonophores we find predatory specialists can evolve into generalists, and that  specialists on one prey type have directly evolved into specialists on other prey types. Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of taxa and characters, and can be used to predict the feeding habits of uncharacterized species.  We conclude that the siphonophores were able to establish as abundant oceanic predators by occupying a variety of trophic niches facilitated by the evolution and diversification of extraordinary prey capture tools on their tentacles.
